\documentclass{article}
\usepackage[letterpaper,margin=0.855in]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{biblatex}
\usepackage{parskip}
\setlength{\parskip}{6pt}
%\bibliographystyle{plain}

%\addbibresource{sample.bib}


\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
 \footnotesize\sffamily
 \yourname\quad\yourdepartment\quad\youruni\quad 
 \textcolor{blue}{aryana.haghjoo@mail.mcgill.ca}}

\newcommand{\soptitle}{Cover Letter}
\newcommand{\yourname}{Aryana Haghjoo}
\newcommand{\youremail}{aryana.haghjoo@mail.mcgill.ca}
\newcommand{\youruni}{Department of Physics, McGill University, Montreal, Qc, Canada}
\newcommand{\statement}[1]{\par\medskip
 \underline{\textcolor{blue}{\textbf{#1:}}}\space
}

\usepackage[
breaklinks,
pdftitle={\yourname - \soptitle},
pdfauthor={\yourname},
unicode
]{hyperref}

 
 

\begin{document}
 \begin{center}\LARGE\soptitle\\
  %\large of \yourname\ (Physics M.Sc. Program Applicant)
 \end{center}
 \vspace{5pt}
 \hrule
 \vspace{1pt}
 \hrule height 1pt
 
 \bigskip
%why do you wanna do a phd? to become a scientist!
%why did you choose physics? both theory and experiment 
%what makes you think you can handle a jon like phd?(my tools to back my motivation)  my solid background ground in theoretical physics, my computational skills, and previous research experiences.
%------------------------start here--------------------------
My motivation to pursue a Ph.D. program is to become an independent scientist who can identify knowledge gaps and collaborate with others to address them. In my point of view, the captivating essence of physics comes from the fact that it has the potential to leverage both ambitious theories and innovative experiments.
I am confident that my qualifications, encompassing a solid background in theoretical physics, computational skills, and prior research experiences, will enable me to excel as a Ph.D. student. The alignment of research interests between your faculty members and my own, coupled with the collaboration opportunities, constitutes my motivation for applying to the Ph.D. program at the Massachusetts Institute of Technology (MIT).\par

My journey in science was initiated in high school. I attended the National Organization for Development of Exceptional Talents (NODET) school, which is designed for talented students in Iran. Beyond standard school work, I voluntarily studied numerous semi-specialized and basic specialized physics books. This served as inspiration to pursue a scientific career.
By the end of high school, after my success of being among the top 0.5 percent of candidates in the national university entrance examination, I continued my studies in Mechanical Engineering at the \textbf{University of Tehran}. However, during the first year, I concluded that I would like to pursue a more fundamental science at the academic level. Therefore, I continued my academic journey by joining the physics department at the \textbf{Sharif University of Technology}, known for hosting one of the top undergraduate physics programs in Iran. Subsequently, I dedicated my life to fulfilling all the requirements of my dream of becoming a scientist. I used this opportunity to take various elective courses and attended several seminars in different branches of physics. As a senior undergraduate student, I challenged my teaching abilities by assisting in a few courses ranging from electromagnetism to introductory cosmology. Based on my outstanding GPA, I was offered the opportunity to get involved in research, as early as the second year of my undergraduate. Working on these research projects not only helped me strengthen my theoretical knowledge but also resulted in developing a firm background in computational methods such as deep learning and simulation of differential equations.\par
With the finishing line of my undergrad in sight, I built a clear vision of my interests in different fields of physics. Consequently, I decided to pursue cosmology and astrophysics. I was eager to participate in a master's program before my Ph.D. to construct a further realistic sense of true research in astrophysics, improve my scientific writing skills, and become more familiar with the challenges of grad life.
After a round of applications, I was offered a full-funded position as a graduate student of physics in \textbf{McGill University} in Canada. Therefore, I traveled across the globe to work under the supervision of \textbf{Jonathan Sievers} (Associate Professor of Observational Cosmology at McGill) and \textbf{Oscar Hernandez} (Adjunct Professor of Theoretical Physics at McGill), where I gained more specific knowledge about the cosmic dawn, reionization, and the study of the global $\mathrm{21cm signal}$. Based on the in-depth computational demands of my thesis project, I had the opportunity to become an expert in parameter estimation algorithms such as Markov Chain Monte Carlo (MCMC). Besides the academic profit, I was educated by the experience of immigration, which resulted in notable personal growth. Moreover, facing independent young adulthood in a foreign environment assisted me in developing a clearer self-awareness.\par

After dedicating over two years to my master's program, I have achieved the personal milestones set for this stage of my academic journey. Consequently, I am eager to commence my Ph.D. to utilize my problem-solving skills. While maintaining my interests in $\mathrm{21cm}$ studies, I am also receptive to exploring other realms of cosmology and astrophysics. With astrophysics entering a data-driven era, I am interested in employing proper computational methods, including Artificial Intelligence (AI), to extract desired signals from raw data and compare them to the predictions of our theoretical models. I believe that my background and prior experience, have prepared me to contribute to cutting-edge research.\par

After finishing the Ph.D., my top priority is to stay in the research. However, my motivations go beyond my research dreams. I wish to use the soft skills I will develop during my Ph.D. (e.g., critical thinking, creativity, and teamwork) to make an impact in all other future roles. I look forward to getting ready for a future where I can learn, contribute, and explore new ideas. I understand this path will not be straightforward, but I strongly believe in my abilities. My passion for learning is the key that keeps me motivated in obstacles.\par

%In recent years, cosmologists have given significant attention to the $21cm$ signal of hydrogen and its great potential in widening our field of view. Throughout my career, I wish to collaborate with other scientists to surf this new window and help extract new physics from this data. The $21cm$ signal will act as an excellent opportunity to advance our current theories of the early universe. 

\end{document}